State of the Art in Scientific Workflow Systems

### 2014-05-28 paper.tex
wings desc

\paragraph{Wings/--} The Workflow instance generation and specialization
(Wings) provides automatic workflow validation and generation based on
high-level workflow templates~\cite{wings2013}. The system receives high-level
workflow specification in the form of Pegasus/DAX workflows and validates them
for correct coordination based on data and resource constraints. It generates
workflows by selecting components, data sets, and parameters in three stages
while eliminating candidates that are not viable. This approach is useful in
the context of desiging complex computational experiments by domain scientists
in that it eases the process of workflow level debugging.

% How does Wings achieve the translation between abstract and concrete workflows?
% What are the internal representations of workflows?
% What are the constraints under which Wings works?
% How is Wings implemented?

%
\paragraph{Swift/Script, Tcl} Swift \cite{swift} is a script-based scientific
workflow environment developed at the University of Chicago and Argonne
National Laboratory. A Swift workflow specified in the Swift scripting language
and is translated to an intermediate XML-based representation and enacted by
the Karajan workflow enactment engine. The SwiftScript language is proposed as
a workflow language founded on a scripting approach that programmers are
familiar with. To make the language data parallel, Swift script generalizes the
use of futures~\cite{futures} for every variables defined in the
script.  Futures are non-blocking assignment variables, using a proxy to ensure
immediate execution of assignment and performing lazy blocking on variable
value accesses only. The systematic use of futures for every variables in the
language makes it completely data-driven: the execution progresses
asynchronously as long as a data access is not blocking. The availability of
data enables blocked thread to restart execution. Swift facilitates a highly
asynchronous workflow execution. Swift supports advanced workflow constructs
such as parallel loops and conditionals. Furthermore Swift supports processing
of explicitly defined arrays of data. Swift workflows take advantage of
POSIX-style shared file system to reuse the data produced by other processors.
Recent advances in Swift:
%Recent advances in Swift: 
\begin{enumerate}
    \item Swift has been shown to run on multiple
        clouds~\cite{ccgrid2013} via its coasters mechanism~\cite{ucc2011}.

>>>>

\paragraph{Wings/--} The Workflow instance generation and specialization
(Wings) provides automatic workflow validation and generation based on
high-level workflow templates~\cite{wings2013}. The system receives high-level
workflow specification in the form of Pegasus/DAX workflows and validates them
for correct coordination based on data and resource constraints. It generates
workflows by selecting components, data sets, and parameters in three stages
while eliminating candidates that are not viable. This approach is useful in
the context of desiging complex computational experiments by domain scientists
in that it eases the process of workflow level debugging. Wings uses W3C's OWL,
Resource Description Framework (RDF), and Semantic Web Rule Language (SWRL) to
represent workflows and their associated constraints.

% How does Wings achieve the translation between abstract and concrete workflows?
% What are the constraints under which Wings works?
% How is Wings implemented?

%
\paragraph{Swift/Script, Tcl} Swift~\cite{swift} is a script-based scientific
workflow environment developed at the University of Chicago and Argonne
National Laboratory. A Swift workflow specified in the Swift scripting language
and is translated to an intermediate XML-based representation and enacted by
the Karajan workflow enactment engine. The SwiftScript language is proposed as
a workflow language founded on a scripting approach that programmers are
familiar with. To make the language data parallel, Swift script generalizes the
use of futures~\cite{futures} for every variables defined in the
script.  Futures are non-blocking assignment variables, using a proxy to ensure
immediate execution of assignment and performing lazy blocking on variable
value accesses only. The systematic use of futures for every variables in the
language makes it completely data-driven: the execution progresses
asynchronously as long as a data access is not blocking. The availability of
data enables blocked thread to restart execution. Swift facilitates a highly
asynchronous workflow execution. Swift supports advanced workflow constructs
such as parallel loops and conditionals. Furthermore Swift supports processing
of explicitly defined arrays of data. Swift workflows take advantage of
POSIX-style shared file system to reuse the data produced by other processors.
Recent advances in Swift:
%Recent advances in Swift: 
\begin{enumerate}
    \item Swift has been shown to run on multiple
        clouds~\cite{ccgrid2013} via its coasters mechanism~\cite{ucc2011}.
